Fluid-mechanical erosion creates anisotropic porous media

### 2022-05-24 docs/PhysicsPaper/StokesErosion.tex
NM
starting sec 3

In order to accurately and efficiently compute the Stokes flow governed by \eqref{eqn:StokesEq}, we reformulate the system as a boundary integral equation (BIE). The boundary integral equations are first formulated in $\RR^2$ and then recast in terms of a Cauchy integral. The Cauchy integral representation enables a barycentric quadrature method to accurately compute the flow intervening between nearly contacting bodies, as is required by the dense configurations examined in this work.

>>>>

  \todo[inline]{Emphasize the complex analysis, rewrite so it isn't
  self-plagirized, compactify which would eliminate, for example,
  equation (15)}
In order to accurately and efficiently compute the Stokes flow governed by \eqref{eqn:StokesEq}, we reformulate the system as a boundary integral equation (BIE). The boundary integral equations are first formulated in $\RR^2$ and then recast in terms of a Cauchy integral. The Cauchy integral representation enables a barycentric quadrature method to accurately compute the flow intervening between nearly contacting bodies, as is required by the dense configurations examined in this work.
